### 2021-04-28 papers/thesis/full/ch2-spherical-harmonics/spherical-harmonics.tex
Minor edit

\remark The results in \bsreflemma{lemma:shxyzrelations} are fairly involved and can be derived via the relationships established for products of Spherical Harmonics and Clebsch-Gordan coefficients as mentioned earlier, but we include this proof so as to generalise to other OPs later on in later chapters.

>>>>

\remark The results in \bsreflemma{lemma:shxyzrelations} are fairly involved and can be derived via the relationships established for products of Spherical Harmonics and Clebsch-Gordan coefficients as mentioned earlier \cite[p231]{sakurai1995modern} but we include this proof so as to generalise to other OPs later on in later chapters.
